---
title: "The Abyss Test: collection overview"
date: today
format:
  html:
    embed-resources: true
    toc: false
execute:
  echo: false
  warning: false
---

<!--
    Rscript data/collected/preprocess.R --long
    quarto render data/collected/overview.qmd

Base R only. The rendered page is git-ignored: out of a handful of people an
aggregate is close to a person.
-->

```{r}
#| label: read

clean <- "clean"
long_file <- file.path(clean, "responses.csv")
wide_file <- file.path(clean, "data.csv")
if (!file.exists(long_file)) {
  stop("No clean/responses.csv: run `Rscript data/collected/preprocess.R --long` first.")
}

long <- read.csv(long_file, stringsAsFactors = FALSE, na.strings = "NA")
wide <- read.csv(wide_file, stringsAsFactors = FALSE, na.strings = "NA")

SEP <- " | "
when <- function(x) as.POSIXct(x, format = "%Y-%m-%dT%H:%M:%OS", tz = "UTC")
```

```{r}
#| label: levels

# Which level an item was on: each level screen (`Level_<N>`) follows the last
# item of its level, so the Nth run of items between screens is the Nth level
# in `levels_walked`.
levels_of <- function(one) {
  row <- wide[wide$participant == one, ]
  walked <- strsplit(row$levels_walked, SEP, fixed = TRUE)[[1]]
  items <- long[long$participant == one, ]
  items <- items[order(items$order), ]
  screen <- grepl("^Level_[0-9]+$", items$key)
  at <- 1 + cumsum(screen) - screen
  data.frame(
    participant = one,
    key = items$key,
    screen = screen,
    level = walked[at],
    position = at,
    onset = when(items$time_onset),
    response = when(items$time_response),
    stringsAsFactors = FALSE
  )
}
items <- do.call(rbind, lapply(unique(wide$participant), levels_of))

# Only finished levels are timed, or the moment somebody gave up would count.
finished <- function(one, key) {
  column <- paste0("QC_", key, "_TimeFinished")
  column %in% names(wide) && !is.na(wide[wide$participant == one, column])
}

# Wall time from the level's first onset to its last response, briefings in.
spans <- do.call(rbind, lapply(split(items[!items$screen, ], list(items$participant[!items$screen], items$level[!items$screen]), drop = TRUE), function(one) {
  data.frame(
    participant = one$participant[1],
    level = one$level[1],
    position = one$position[1],
    minutes = as.numeric(difftime(max(one$response, na.rm = TRUE), min(one$onset, na.rm = TRUE), units = "mins")),
    finished = finished(one$participant[1], one$level[1]),
    stringsAsFactors = FALSE
  )
}))
done <- spans[spans$finished, ]

screens <- items[items$screen & !is.na(items$onset) & !is.na(items$response), ]
screens$minutes <- as.numeric(difftime(screens$response, screens$onset, units = "mins"))
```

```{r}
#| label: summary

summarise <- function(frame, unit = "minutes") {
  if (!nrow(frame)) return(data.frame(level = character(), n = integer(), median = numeric(), min = numeric(), max = numeric()))
  do.call(rbind, lapply(split(frame, frame$level), function(one) {
    time <- one[[unit]]
    data.frame(level = one$level[1], n = nrow(one), median = median(time), min = min(time), max = max(time))
  }))
}

# Longer than this on one level, or on its results, is somebody who went away
# and came back: kept out of the times, and counted on the page instead.
BREAK <- 45
timed <- done[done$minutes <= BREAK, ]
screens$seconds <- screens$minutes * 60
read <- screens[screens$minutes <= BREAK, ]
breaks <- sum(done$minutes > BREAK) + sum(screens$minutes > BREAK)

# Every finished level gets a row, even one whose only time was a break.
rows <- function(summary, levels) {
  summary <- summary[match(levels, summary$level), ]
  summary$level <- levels
  summary$n[is.na(summary$n)] <- 0L
  rownames(summary) <- NULL
  summary
}

# In the order levels were met on average: no one person's order is the order.
where <- tapply(done$position, done$level, mean)
met <- names(sort(where))
table <- rows(summarise(timed), met)
reading <- rows(summarise(read, "seconds"), met)

# A finished level with no screen in the file: the way on is only staged once
# pressed, so the tab was closed on its results.
left <- paste(screens$participant, screens$level)
stopped_on <- done[!paste(done$participant, done$level) %in% left, ]
reading$closed <- as.integer(table(factor(stopped_on$level, levels = table$level)))
```

`r nrow(wide)` runs: `r sum(wide$completed)` finished, `r sum(!wide$completed)` stopped partway.

## How long a level takes

Answering: first item shown to last answer, finished levels only. Results screen: until the way on was pressed. Anything over `r BREAK` minutes is a break rather than a time and is left out of both (`r breaks` so far). Total: the levels' medians added up (and their minima and maxima, for the range), which is how long the whole test would take somebody typical on every level, over the levels timed so far.

```{r}
#| label: plot
#| fig-width: 8
#| fig-height: !expr max(2.4, 0.55 * nrow(table) + 1.4)

ANSWERING <- c(line = "#a58bff", dot = "#7c5cff80", median = "#5b3fd6")
RESULTS <- c(line = "#e8c77a", dot = "#d9a44180", median = "#b07d1c")

panel <- function(summary, runs, unit, title, colours, named) {
  y <- rev(seq_len(nrow(summary)))
  has <- summary$n > 0
  top <- if (any(has)) max(summary$max[has]) else 1
  par(mar = c(4, if (named) 9 else 1.5, 2, 1.5))
  plot(NULL, xlim = c(0, top * 1.1), ylim = c(0.5, nrow(summary) + 0.5),
       yaxt = "n", xlab = tools::toTitleCase(unit), ylab = "", bty = "n")
  title(main = title, font.main = 1, cex.main = 1, adj = 0)
  if (named) axis(2, at = y, labels = summary$level, las = 1, tick = FALSE)
  abline(h = y, col = "grey93")
  segments(summary$min[has], y[has], summary$max[has], y[has], lwd = 3, col = colours["line"])
  points(runs[[unit]], y[match(runs$level, summary$level)], pch = 16, cex = 0.7, col = colours["dot"])
  points(summary$median[has], y[has], pch = 21, bg = colours["median"], col = "white", cex = 1.6)
}

if (nrow(table)) {
  # Wider by the names, so the two plots come out the same width.
  op <- par(no.readonly = TRUE)
  layout(matrix(1:2, 1), widths = c(1.45, 1))
  panel(table, timed, "minutes", "Answering", ANSWERING, TRUE)
  panel(reading, read[read$level %in% table$level, ], "seconds", "Results screen", RESULTS, FALSE)
  par(op)
} else {
  cat("No level has been finished yet.")
}
```

```{r}
#| label: table

span <- function(summary, digits = 1) {
  ifelse(summary$n > 0, sprintf("%.*f to %.*f", digits, summary$min, digits, summary$max), "")
}
middle <- function(summary, digits = 1) ifelse(summary$n > 0, sprintf("%.*f", digits, summary$median), "")
shown <- data.frame(
  Level = table$level,
  `Answering: n` = table$n,
  `median (min)` = middle(table),
  `range (min)` = span(table),
  `Results: n` = reading$n,
  `median (s)` = middle(reading, 0),
  `range (s)` = span(reading, 0),
  `Closed on results` = reading$closed,
  check.names = FALSE
)

# What the whole test would take somebody typical on every level: the levels'
# medians (and minima, and maxima) added up, over the levels timed so far.
added <- function(summary, digits) {
  has <- summary$n > 0
  if (!any(has)) return(c(median = "", range = ""))
  c(median = sprintf("%.*f", digits, sum(summary$median[has])),
    range = sprintf("%.*f to %.*f", digits, sum(summary$min[has]), digits, sum(summary$max[has])))
}
if (nrow(table)) {
  answering <- added(table, 1)
  results <- added(reading, 0)
  shown <- rbind(shown, data.frame(
    Level = sprintf("**Total** (%d levels)", sum(table$n > 0)),
    `Answering: n` = "",
    `median (min)` = answering[["median"]],
    `range (min)` = answering[["range"]],
    `Results: n` = "",
    `median (s)` = results[["median"]],
    `range (s)` = results[["range"]],
    `Closed on results` = sum(reading$closed),
    check.names = FALSE
  ))
}
knitr::kable(shown, align = "lrrrrrrr")
```

## Ratings


```{r}
#| label: liked
#| fig-width: 7
#| fig-height: 5

# Stars are filed under the level's key, which is what `levels_walked` holds.
stars <- do.call(rbind, lapply(table$level, function(key) {
  column <- paste0("Rating_", key)
  given <- if (column %in% names(wide)) wide[[column]] else numeric()
  given <- given[!is.na(given)]
  data.frame(level = key, rated = length(given), stars = if (length(given)) median(given) else NA)
}))
liked <- cbind(table[, c("level", "median")], stars[, c("rated", "stars")])
liked <- liked[table$n > 0 & liked$rated > 0, ]

if (nrow(liked)) {
  par(mar = c(4, 4, 1, 1))
  plot(liked$median, liked$stars, xlim = c(0, max(liked$median) * 1.25), ylim = c(1, 5),
       pch = 21, bg = ANSWERING["median"], col = "white", cex = 1.8, bty = "n", las = 1,
       xlab = "Median answering time (minutes)", ylab = "Median rating (stars)")
  text(liked$median, liked$stars, sprintf("%s (%d)", liked$level, liked$rated), pos = 4, cex = 0.8, col = "grey30")
} else {
  cat("No level has both a time and a rating yet.")
}
```

## Answers by level

```{r}
#| label: codebook

# Every item's scale, read out of content/ by the same reader the synthetic
# workbench and the deck use, so no labels are restated here.
MIN_RUNS <- 2
NOT_SCALES <- c("icar16") # right or wrong, and the values are positions in a list
codebook <- tryCatch(
  jsonlite::fromJSON(paste(system2("bun", file.path("..", "synthetic", "codebook.js"), stdout = TRUE), collapse = "\n"),
                     simplifyVector = FALSE),
  error = function(e) stop("Could not run `bun data/synthetic/codebook.js`: ", conditionMessage(e))
)
level_keys <- vapply(codebook$levels, function(one) one$key, "")

scale_items <- Filter(function(item) {
  item$type %in% c("choice", "slider", "curve") && is.null(item$check) &&
    !grepl("^demographics", item$questionnaire) && !item$questionnaire %in% NOT_SCALES &&
    !is.null(item$lowest) && !is.null(item$highest) && item$highest > item$lowest
}, codebook$items)

# What was on screen, back into the value behind it: the option's words, else
# the label written on its circle, else the number itself. An escape option
# ("Something else") is no place on the scale.
unread <- character()
reach <- function(item, given) {
  if (item$type %in% c("slider", "curve")) {
    value <- suppressWarnings(as.numeric(sub("%$", "", given)))
  } else {
    said <- vapply(item$options, function(one) {
      if (!is.null(one$text)) one$text else if (!is.null(one$label)) one$label else as.character(one$value)
    }, "")
    values <- vapply(item$options, function(one) if (isTRUE(one$custom)) NA_real_ else as.numeric(one$value), 0)
    given <- as.character(given)
    # The MINT's labels are drawn per run (`formatMint`) and the codebook holds
    # one draw, so a bare number is read as the value it was under the other.
    numbers <- vapply(item$options, function(one) as.character(one$value), "")
    value <- ifelse(given %in% said, values[match(given, said)], values[match(given, numbers)])
    stray <- !is.na(given) & !given %in% c(said, numbers)
    if (any(stray)) unread <<- c(unread, paste0(item$key, ": ", given[stray]))
  }
  (value - item$lowest) / (item$highest - item$lowest)
}

# A scale is the key without its last part (or its first part, of two).
scale_of <- function(key) {
  parts <- strsplit(key, "_", fixed = TRUE)[[1]]
  paste(parts[-length(parts)], collapse = "_")
}

by_level <- list()
for (item in scale_items) {
  if (!item$key %in% names(wide)) next
  level <- level_keys[item$level]
  column <- setNames(data.frame(reach(item, wide[[item$key]])), item$key)
  by_level[[level]] <- if (is.null(by_level[[level]])) column else cbind(by_level[[level]], column)
}
by_level <- by_level[intersect(level_keys, names(by_level))]
runs_on <- vapply(by_level, function(frame) sum(rowSums(!is.na(frame)) > 0), 0)

# Answers under keys the codebook no longer has: renamed since they were saved.
answered_keys <- setdiff(names(wide)[grepl("^[A-Z][A-Za-z0-9]*_", names(wide))], grep("_RT$", names(wide), value = TRUE))
stale <- setdiff(answered_keys, vapply(codebook$items, function(item) item$key, ""))
stale <- stale[!grepl("^(QC|Feedback|Rating|Level)_", stale)]
```

One radar per level that at least `r MIN_RUNS` runs have answered: a box plot along each ray (median, quartiles, whiskers to 1.5 IQR, points beyond), each item as a share of its own scale, as answered (reversed items not flipped). Nothing joins the rays: neighbouring items are not a continuum. Demographics, free text and right-answer items are left out.

```{r}
#| label: radar

radar <- function(reaches, title) {
  reaches <- reaches[, sort(names(reaches)), drop = FALSE]
  keys <- names(reaches)
  k <- length(keys)
  angle <- pi / 2 - 2 * pi * (seq_len(k) - 1) / k
  at <- function(r) cbind(r * cos(angle), r * sin(angle))
  scales <- vapply(keys, scale_of, "")
  hue <- hcl.colors(length(unique(scales)), "Dark 3")[match(scales, unique(scales))]

  op <- par(mar = c(1, 1, 2, 1), xpd = TRUE)
  on.exit(par(op))
  plot(NULL, xlim = c(-1.5, 1.5), ylim = c(-1.4, 1.4), asp = 1, axes = FALSE, xlab = "", ylab = "")
  title(main = title, font.main = 1, cex.main = 1.1, adj = 0)
  for (r in c(0.25, 0.5, 0.75, 1)) {
    polygon(at(rep(r, k)), border = if (r == 0.5) "grey75" else "grey88", lty = if (r == 0.5) 2 else 1)
  }
  segments(0, 0, cos(angle), sin(angle), col = "grey90")
  text(0.02, c(0.5, 1) + 0.03, c("middle", "top"), cex = 0.6, col = "grey55", adj = 0)

  # A box plot lying along each ray: whiskers, the box between the quartiles
  # as a strip across the ray, the median a bar across it, outliers as points.
  width <- min(0.035, 0.8 / k) # half a box: at most a quarter of the gap between rays at the rim
  for (i in seq_len(k)) {
    given <- reaches[[i]]
    given <- given[!is.na(given)]
    if (!length(given)) next
    stats <- boxplot.stats(given)
    five <- stats$stats
    along <- c(cos(angle[i]), sin(angle[i]))
    across <- c(-along[2], along[1])
    segments(five[1] * along[1], five[1] * along[2], five[5] * along[1], five[5] * along[2], col = hue[i], lwd = 1.2)
    box <- rbind(five[2] * along + width * across, five[4] * along + width * across,
                 five[4] * along - width * across, five[2] * along - width * across)
    polygon(box, col = adjustcolor(hue[i], 0.3), border = hue[i], lwd = 1)
    bar <- rbind(five[3] * along + 1.6 * width * across, five[3] * along - 1.6 * width * across)
    segments(bar[1, 1], bar[1, 2], bar[2, 1], bar[2, 2], col = hue[i], lwd = 2.4)
    if (length(stats$out)) points(stats$out * along[1], stats$out * along[2], pch = 16, cex = 0.6, col = hue[i])
  }

  # Read outwards, never upside down.
  degrees <- angle * 180 / pi
  flip <- cos(angle) < 0
  place <- at(rep(1.06, k))
  for (i in seq_len(k)) {
    text(place[i, 1], place[i, 2], sub("^Opinion_", "", keys[i]), cex = if (k > 30) 0.62 else 0.75, col = hue[i],
         srt = if (flip[i]) degrees[i] + 180 else degrees[i], adj = if (flip[i]) 1 else 0)
  }
}
```

```{r}
#| label: radars
#| results: asis
#| fig-width: 8.5
#| fig-height: 8.5

plotted <- names(runs_on)[runs_on >= MIN_RUNS]
if (!length(plotted)) cat("No level has been answered by", MIN_RUNS, "runs yet.\n")
for (level in plotted) {
  cat("\n\n### ", level, "\n\n", sep = "")
  radar(by_level[[level]], sprintf("%s (%d runs)", level, runs_on[[level]]))
  cat("\n\n")
}
waiting <- names(runs_on)[runs_on < MIN_RUNS]
if (length(waiting)) {
  cat("\n\nNot drawn yet (fewer than ", MIN_RUNS, " runs): ",
      paste(sprintf("%s (%d)", waiting, runs_on[waiting]), collapse = ", "), ".\n", sep = "")
}
```

```{r}
#| label: radars-said
#| results: asis

if (length(unread)) {
  cat("\n\n**Answers not read** (words matching no option of the item in the codebook): ", paste(unique(unread), collapse = "; "), "\n", sep = "")
}
if (length(stale)) {
  cat("\n\n**Keys no longer in the codebook**, left out: ", paste(stale, collapse = ", "), "\n", sep = "")
}
```
