---
title: "The Abyss Test: collection overview"
date: today
format:
  html:
    embed-resources: true
    toc: false
execute:
  echo: false
  warning: false
---

<!--
    Rscript data/collected/preprocess.R --long
    quarto render data/collected/overview.qmd

Base R only. The rendered page is git-ignored: out of a handful of people an
aggregate is close to a person.
-->

```{r}
#| label: read

clean <- "clean"
long_file <- file.path(clean, "responses.csv")
wide_file <- file.path(clean, "data.csv")
if (!file.exists(long_file)) {
  stop("No clean/responses.csv: run `Rscript data/collected/preprocess.R --long` first.")
}

long <- read.csv(long_file, stringsAsFactors = FALSE, na.strings = "NA")
wide <- read.csv(wide_file, stringsAsFactors = FALSE, na.strings = "NA")

SEP <- " | "
when <- function(x) as.POSIXct(x, format = "%Y-%m-%dT%H:%M:%OS", tz = "UTC")

# Every item and level, read out of content/ by the same reader the synthetic
# workbench and the deck use, so no labels are restated here.
codebook <- tryCatch(
  jsonlite::fromJSON(paste(system2("bun", file.path("..", "synthetic", "codebook.js"), stdout = TRUE), collapse = "\n"),
                     simplifyVector = FALSE),
  error = function(e) stop("Could not run `bun data/synthetic/codebook.js`: ", conditionMessage(e))
)
level_keys <- vapply(codebook$levels, function(one) one$key, "")
level_names <- vapply(codebook$levels, function(one) one$name, "")
```

```{r}
#| label: levels

# Which level an item was on: each level screen (`Level_<N>`) follows the last
# item of its level, so the Nth run of items between screens is the Nth level
# in `levels_walked`.
levels_of <- function(one) {
  row <- wide[wide$participant == one, ]
  walked <- strsplit(row$levels_walked, SEP, fixed = TRUE)[[1]]
  items <- long[long$participant == one, ]
  items <- items[order(items$order), ]
  # A run that pressed Start and answered nothing has a row and no items.
  if (!nrow(items)) return(NULL)
  screen <- grepl("^Level_[0-9]+$", items$key)
  at <- 1 + cumsum(screen) - screen
  data.frame(
    participant = one,
    key = items$key,
    screen = screen,
    level = walked[at],
    position = at,
    onset = when(items$time_onset),
    response = when(items$time_response),
    stringsAsFactors = FALSE
  )
}
items <- do.call(rbind, lapply(unique(wide$participant), levels_of))

# Only finished levels are timed, or the moment somebody gave up would count.
finished <- function(one, key) {
  column <- paste0("QC_", key, "_TimeFinished")
  column %in% names(wide) && !is.na(wide[wide$participant == one, column])
}

# Wall time from the level's first onset to its last response, briefings in.
spans <- do.call(rbind, lapply(split(items[!items$screen, ], list(items$participant[!items$screen], items$level[!items$screen]), drop = TRUE), function(one) {
  data.frame(
    participant = one$participant[1],
    level = one$level[1],
    position = one$position[1],
    minutes = as.numeric(difftime(max(one$response, na.rm = TRUE), min(one$onset, na.rm = TRUE), units = "mins")),
    finished = finished(one$participant[1], one$level[1]),
    stringsAsFactors = FALSE
  )
}))
done <- spans[spans$finished, ]

screens <- items[items$screen & !is.na(items$onset) & !is.na(items$response), ]
screens$minutes <- as.numeric(difftime(screens$response, screens$onset, units = "mins"))
```

```{r}
#| label: summary

summarise <- function(frame, unit = "minutes") {
  if (!nrow(frame)) return(data.frame(level = character(), n = integer(), median = numeric(), min = numeric(), max = numeric()))
  do.call(rbind, lapply(split(frame, frame$level), function(one) {
    time <- one[[unit]]
    data.frame(level = one$level[1], n = nrow(one), median = median(time), min = min(time), max = max(time))
  }))
}

# Longer than this on one level, or on its results, is somebody who went away
# and came back: kept out of the times, and counted on the page instead.
BREAK <- 45
timed <- done[done$minutes <= BREAK, ]
screens$seconds <- screens$minutes * 60
read <- screens[screens$minutes <= BREAK, ]
breaks <- sum(done$minutes > BREAK) + sum(screens$minutes > BREAK)

# Every finished level gets a row, even one whose only time was a break.
rows <- function(summary, levels) {
  summary <- summary[match(levels, summary$level), ]
  summary$level <- levels
  summary$n[is.na(summary$n)] <- 0L
  rownames(summary) <- NULL
  summary
}

# In the order levels were met on average: no one person's order is the order.
where <- tapply(done$position, done$level, mean)
met <- names(sort(where))
table <- rows(summarise(timed), met)
reading <- rows(summarise(read, "seconds"), met)

# A finished level with no screen in the file: the way on is only staged once
# pressed, so the tab was closed on its results.
left <- paste(screens$participant, screens$level)
stopped_on <- done[!paste(done$participant, done$level) %in% left, ]
reading$closed <- as.integer(table(factor(stopped_on$level, levels = table$level)))
```

`r nrow(wide)` runs: `r sum(wide$completed)` finished, `r sum(!wide$completed)` stopped partway.

## How long a level takes

Answering: first item shown to last answer, finished levels only. Results screen: until the way on was pressed. Anything over `r BREAK` minutes is a break rather than a time and is left out of both (`r breaks` so far). Total: the levels' medians added up (and their minima and maxima, for the range), which is how long the whole test would take somebody typical on every level, over the levels timed so far.

```{r}
#| label: plot
#| fig-width: 8
#| fig-height: !expr max(2.4, 0.55 * nrow(table) + 1.4)

ANSWERING <- c(line = "#a58bff", dot = "#7c5cff80", median = "#5b3fd6")
RESULTS <- c(line = "#e8c77a", dot = "#d9a44180", median = "#b07d1c")

panel <- function(summary, runs, unit, title, colours, named) {
  y <- rev(seq_len(nrow(summary)))
  has <- summary$n > 0
  top <- if (any(has)) max(summary$max[has]) else 1
  par(mar = c(4, if (named) 9 else 1.5, 2, 1.5))
  plot(NULL, xlim = c(0, top * 1.1), ylim = c(0.5, nrow(summary) + 0.5),
       yaxt = "n", xlab = tools::toTitleCase(unit), ylab = "", bty = "n")
  title(main = title, font.main = 1, cex.main = 1, adj = 0)
  if (named) axis(2, at = y, labels = summary$level, las = 1, tick = FALSE)
  abline(h = y, col = "grey93")
  segments(summary$min[has], y[has], summary$max[has], y[has], lwd = 3, col = colours["line"])
  points(runs[[unit]], y[match(runs$level, summary$level)], pch = 16, cex = 0.7, col = colours["dot"])
  points(summary$median[has], y[has], pch = 21, bg = colours["median"], col = "white", cex = 1.6)
}

if (nrow(table)) {
  # Wider by the names, so the two plots come out the same width.
  op <- par(no.readonly = TRUE)
  layout(matrix(1:2, 1), widths = c(1.45, 1))
  panel(table, timed, "minutes", "Answering", ANSWERING, TRUE)
  panel(reading, read[read$level %in% table$level, ], "seconds", "Results screen", RESULTS, FALSE)
  par(op)
} else {
  cat("No level has been finished yet.")
}
```

```{r}
#| label: table

span <- function(summary, digits = 1) {
  ifelse(summary$n > 0, sprintf("%.*f to %.*f", digits, summary$min, digits, summary$max), "")
}
middle <- function(summary, digits = 1) ifelse(summary$n > 0, sprintf("%.*f", digits, summary$median), "")
shown <- data.frame(
  Level = table$level,
  `Answering: n` = table$n,
  `median (min)` = middle(table),
  `range (min)` = span(table),
  `Results: n` = reading$n,
  `median (s)` = middle(reading, 0),
  `range (s)` = span(reading, 0),
  `Closed on results` = reading$closed,
  check.names = FALSE
)

# What the whole test would take somebody typical on every level: the levels'
# medians (and minima, and maxima) added up, over the levels timed so far.
added <- function(summary, digits) {
  has <- summary$n > 0
  if (!any(has)) return(c(median = "", range = ""))
  c(median = sprintf("%.*f", digits, sum(summary$median[has])),
    range = sprintf("%.*f to %.*f", digits, sum(summary$min[has]), digits, sum(summary$max[has])))
}
if (nrow(table)) {
  answering <- added(table, 1)
  results <- added(reading, 0)
  shown <- rbind(shown, data.frame(
    Level = sprintf("**Total** (%d levels)", sum(table$n > 0)),
    `Answering: n` = "",
    `median (min)` = answering[["median"]],
    `range (min)` = answering[["range"]],
    `Results: n` = "",
    `median (s)` = results[["median"]],
    `range (s)` = results[["range"]],
    `Closed on results` = sum(reading$closed),
    check.names = FALSE
  ))
}
knitr::kable(shown, align = "lrrrrrrr")
```

## Ratings


```{r}
#| label: liked
#| fig-width: 7
#| fig-height: 5

# Stars are filed under the level's key, which is what `levels_walked` holds.
stars <- do.call(rbind, lapply(table$level, function(key) {
  column <- paste0("Rating_", key)
  given <- if (column %in% names(wide)) wide[[column]] else numeric()
  given <- given[!is.na(given)]
  data.frame(level = key, rated = length(given), stars = if (length(given)) median(given) else NA)
}))
liked <- cbind(table[, c("level", "median")], stars[, c("rated", "stars")])
liked <- liked[table$n > 0 & liked$rated > 0, ]

if (nrow(liked)) {
  par(mar = c(4, 4, 1, 1))
  plot(liked$median, liked$stars, xlim = c(0, max(liked$median) * 1.25), ylim = c(1, 5),
       pch = 21, bg = ANSWERING["median"], col = "white", cex = 1.8, bty = "n", las = 1,
       xlab = "Median answering time (minutes)", ylab = "Median rating (stars)")
  text(liked$median, liked$stars, sprintf("%s (%d)", liked$level, liked$rated), pos = 4, cex = 0.8, col = "grey30")
} else {
  cat("No level has both a time and a rating yet.")
}
```

## Choices

```{r}
#| label: choices

# Every fork choice in the runs, one row each. A file from September 2026 on
# says how the cards stood and which was recommended (`Level_<N>_Offered`,
# `_Recommended`, `_Chosen`, in keys). One from before says only what was taken
# and what was passed over, in the words on the cards (`Level_<N>`, the taken
# first), so where its cards stood and which was recommended are unknown; its
# names are read back to keys through the codebook, which holds today's names.
key_of <- setNames(level_keys, level_names)
unnamed <- character()
picks <- list()
column <- function(name, row) if (name %in% names(wide)) as.character(wide[[name]][row]) else NA_character_
for (screen in grep("^Level_[0-9]+$", names(wide), value = TRUE)) {
  for (row in seq_len(nrow(wide))) {
    offered <- column(paste0(screen, "_Offered"), row)
    if (!is.na(offered)) {
      picks[[length(picks) + 1]] <- list(
        participant = wide$participant[row], screen = screen, placed = TRUE,
        offered = strsplit(offered, SEP, fixed = TRUE)[[1]],
        recommended = column(paste0(screen, "_Recommended"), row),
        chosen = column(paste0(screen, "_Chosen"), row)
      )
      next
    }
    said <- column(screen, row)
    if (is.na(said) || !grepl(SEP, said, fixed = TRUE)) next # the one button, not a choice
    words <- strsplit(said, SEP, fixed = TRUE)[[1]]
    keys <- unname(key_of[words])
    if (anyNA(keys)) {
      unnamed <- c(unnamed, words[is.na(keys)])
      next
    }
    picks[[length(picks) + 1]] <- list(
      participant = wide$participant[row], screen = screen, placed = FALSE,
      offered = keys, recommended = NA_character_, chosen = keys[1]
    )
  }
}

# The same choices one row a card: what was offered, how many beside it, where
# it stood, whether it was the one recommended and whether it was taken.
cards <- do.call(rbind, lapply(seq_along(picks), function(i) {
  one <- picks[[i]]
  k <- length(one$offered)
  data.frame(
    choice = i, participant = one$participant, level = one$offered, k = k,
    position = if (one$placed) seq_len(k) else NA_integer_,
    recommended = if (is.na(one$recommended)) NA else one$offered == one$recommended,
    chosen = one$offered == one$chosen,
    stringsAsFactors = FALSE
  )
}))
n_choices <- length(picks)
n_known <- sum(vapply(picks, function(one) !is.na(one$recommended), TRUE))
```

`r n_choices` choices by `r length(unique(vapply(picks, function(one) one$participant, "")))` runs, `r n_known` of them saying where the cards stood and which was recommended. A level offered beside *k* others would be taken 1 in *k* times by chance, so **expected** below is that chance added up over every time the level was offered, and **lift** is the times taken over it: 1 is chance, 2 is twice as often. All of it is blind: nobody has taken a level when it is offered, only seen its name, its length and its blurred results.

```{r}
#| label: choices-pull
#| results: asis

# The two pulls that have nothing to do with the level: the card marked
# "Recommended next", and where a card stood.
if (n_known) {
  known <- cards[!is.na(cards$recommended) & cards$recommended, ]
  cat(sprintf("**The recommendation**: taken in %d of %d choices (%.0f%%), where chance would take it in %.0f%%.\n\n",
              sum(known$chosen), nrow(known), 100 * mean(known$chosen), 100 * mean(1 / known$k)))
  placed <- cards[!is.na(cards$position), ]
  where <- do.call(rbind, lapply(split(placed, placed$position), function(one) {
    data.frame(Card = one$position[1], Offered = nrow(one), Taken = sum(one$chosen),
               Share = sprintf("%.0f%%", 100 * mean(one$chosen)), Chance = sprintf("%.0f%%", 100 * mean(1 / one$k)))
  }))
  cat("**Where the card stood** (1 is the left, or the top where the cards stack):\n\n")
  print(knitr::kable(where, row.names = FALSE, align = "rrrrr"))
} else {
  cat("No choice yet says which card was recommended or where the cards stood.\n")
}
```

```{r}
#| label: choices-levels

if (n_choices) {
  popularity <- do.call(rbind, lapply(split(cards, cards$level), function(one) {
    unmarked <- one[!is.na(one$recommended) & !one$recommended, ]
    data.frame(
      level = one$level[1],
      offered = nrow(one),
      taken = sum(one$chosen),
      expected = sum(1 / one$k),
      recommended = if (all(is.na(one$recommended))) NA else sum(one$recommended, na.rm = TRUE),
      unmarked_offered = nrow(unmarked),
      unmarked_taken = sum(unmarked$chosen),
      stringsAsFactors = FALSE
    )
  }))
  popularity$lift <- popularity$taken / popularity$expected
  popularity <- popularity[order(-popularity$lift), ]
  knitr::kable(data.frame(
    Level = popularity$level,
    Offered = popularity$offered,
    Taken = popularity$taken,
    Expected = sprintf("%.1f", popularity$expected),
    Lift = sprintf("%.2f", popularity$lift),
    Recommended = ifelse(is.na(popularity$recommended), "", popularity$recommended),
    `Taken when not recommended` = ifelse(popularity$unmarked_offered > 0,
                                          sprintf("%d of %d", popularity$unmarked_taken, popularity$unmarked_offered), ""),
    check.names = FALSE
  ), align = "lrrrrrr")
} else {
  cat("No level has been chosen over another yet.")
}
```

Head to head: the times the row's level was taken while the column's was on offer beside it, out of the times the two were offered together.

```{r}
#| label: choices-pairs

if (n_choices) {
  met <- sort(unique(cards$level))
  cell <- matrix("", length(met), length(met), dimnames = list(met, met))
  for (a in met) for (b in met) {
    if (a == b) next
    both <- Filter(function(one) all(c(a, b) %in% one$offered), picks)
    if (length(both)) cell[a, b] <- sprintf("%d/%d", sum(vapply(both, function(one) one$chosen == a, TRUE)), length(both))
  }
  knitr::kable(cell, align = "c")
}
```

```{r}
#| label: choices-model
#| results: asis

# **A conditional logit**: each choice is one card taken out of those offered,
# with a card's pull the level's own strength (summing to 0 over the levels)
# plus one shared pull for being the card recommended. That separates the
# levels from the recommendation, which the lift above cannot, and it is only
# identified where the recommendation varies across levels — so on the choices
# that say which card it was, and only once there are enough of them. A light
# ridge (`RIDGE`) keeps a level that has never been taken, or always has, from
# running off to infinity on a handful of choices; it is not a prior anybody
# should read anything into.
MIN_CHOICES <- 30
RIDGE <- 0.1
strength <- NULL
fit_choices <- function(cards) {
  levels <- sort(unique(cards$level))
  n <- length(levels)
  at <- match(cards$level, levels)
  marked <- as.numeric(cards$recommended)
  by_choice <- split(seq_len(nrow(cards)), cards$choice)
  pull <- function(par) c(par[seq_len(n - 1)], -sum(par[seq_len(n - 1)]))[at] + par[n] * marked
  loss <- function(par) {
    u <- pull(par)
    -sum(vapply(by_choice, function(i) sum(u[i][cards$chosen[i]]) - log(sum(exp(u[i]))), 0)) + RIDGE * sum(par^2) / 2
  }
  fit <- optim(rep(0, n), loss, method = "BFGS", hessian = TRUE)
  cover <- tryCatch(solve(fit$hessian), error = function(e) matrix(NA, n, n))
  # The last level's strength is minus the sum of the others', so its
  # uncertainty is theirs added up, covariances and all.
  free <- seq_len(n - 1)
  last <- c(rep(-1, n - 1), 0)
  data.frame(
    level = c(levels, "(recommended)"),
    estimate = c(fit$par[free], -sum(fit$par[free]), fit$par[n]),
    se = sqrt(c(diag(cover)[free], drop(t(last) %*% cover %*% last), cover[n, n])),
    stringsAsFactors = FALSE
  )
}

modelled <- if (n_choices) cards[cards$choice %in% which(vapply(picks, function(one) !is.na(one$recommended), TRUE)), ] else NULL
if (!is.null(modelled) && length(unique(modelled$choice)) >= MIN_CHOICES) {
  fitted <- fit_choices(modelled)
  strength <- fitted[fitted$level != "(recommended)", ]
  pulled <- fitted[fitted$level == "(recommended)", ]
  cat(sprintf("**Blind strength**, from %d choices. Being the recommended card multiplies the odds of being taken by %.1f (%.1f to %.1f). A level's strength is its log odds of being taken against an average level on a card with the same mark:\n\n",
              length(unique(modelled$choice)), exp(pulled$estimate),
              exp(pulled$estimate - 1.96 * pulled$se), exp(pulled$estimate + 1.96 * pulled$se)))
  strength <- strength[order(-strength$estimate), ]
  print(knitr::kable(data.frame(Level = strength$level, Strength = sprintf("%+.2f", strength$estimate),
                                SE = sprintf("%.2f", strength$se)), row.names = FALSE, align = "lrr"))
} else {
  cat(sprintf("\n\nThe model separating a level's own pull from the recommendation waits for %d choices that say which card was recommended (%d so far); until then the lift above stands in for it.\n",
              MIN_CHOICES, if (is.null(modelled)) 0L else length(unique(modelled$choice))))
}
```

### Chosen against liked

How often a level is taken blind, against how many stars it gets once it has been taken: above the line, a level people like more than its card promised; below it, one that promised more than it gave. Blind popularity is the model's strength where there is one and the log of the lift where there is not.

```{r}
#| label: choices-liked
#| fig-width: 7
#| fig-height: 5

if (n_choices) {
  blind <- if (!is.null(strength)) setNames(strength$estimate, strength$level) else
    setNames(log((popularity$taken + 0.5) / (popularity$expected + 0.5)), popularity$level)
  score <- vapply(names(blind), function(key) {
    given <- if (paste0("Rating_", key) %in% names(wide)) wide[[paste0("Rating_", key)]] else numeric()
    if (any(!is.na(given))) mean(given, na.rm = TRUE) else NA_real_
  }, 0)
  rated_n <- vapply(names(blind), function(key) {
    column <- paste0("Rating_", key)
    if (column %in% names(wide)) sum(!is.na(wide[[column]])) else 0L
  }, 0L)
  both <- !is.na(score)
  if (sum(both) >= 2) {
    x <- blind[both]
    y <- score[both]
    par(mar = c(4, 4, 1, 1))
    plot(x, y, ylim = c(1, 5), xlim = range(x) + c(-0.3, 0.8) * diff(range(x)) * 0.5, pch = 21,
         bg = RESULTS["median"], col = "white", cex = 1.8, bty = "n", las = 1,
         xlab = if (is.null(strength)) "Blind popularity (log lift)" else "Blind strength (log odds)",
         ylab = "Mean rating (stars)")
    text(x, y, sprintf("%s (%d)", names(x), rated_n[both]), pos = 4, cex = 0.8, col = "grey30")
    if (sum(both) >= 3) {
      line <- lm(y ~ x)
      abline(line, col = "grey70", lty = 2)
      gap <- sort(residuals(line), decreasing = TRUE)
    }
  } else {
    cat("Fewer than two chosen levels have been rated yet.")
  }
}
```

```{r}
#| label: choices-said
#| results: asis

# How far each level's stars sit from what its blind popularity predicts.
if (exists("gap")) {
  print(knitr::kable(data.frame(Level = names(gap), `Stars above expectation` = sprintf("%+.2f", gap), check.names = FALSE),
                     row.names = FALSE, align = "lr"))
}
if (length(unnamed)) {
  cat("\n\n**Cards not read** (a level name the codebook no longer has, so an older choice was left out): ",
      paste(unique(unnamed), collapse = "; "), "\n", sep = "")
}
```

## Answers by level

```{r}
#| label: codebook

# Every item's scale, out of the codebook read at the top.
MIN_RUNS <- 2
NOT_SCALES <- c("icar16") # right or wrong, and the values are positions in a list

scale_items <- Filter(function(item) {
  item$type %in% c("choice", "slider", "curve") && is.null(item$check) &&
    !grepl("^demographics", item$questionnaire) && !item$questionnaire %in% NOT_SCALES &&
    !is.null(item$lowest) && !is.null(item$highest) && item$highest > item$lowest
}, codebook$items)

# What was on screen, back into the value behind it: the option's words, else
# the label written on its circle, else the number itself. An escape option
# ("Something else") is no place on the scale.
unread <- character()
reach <- function(item, given) {
  # The MINT is asked in one of three formats a run (`format_mint`), and the
  # codebook describes only the first: on the circles numbered 0 to 6 and on the
  # slider what is saved is the value itself, and on the circles numbered -3 to
  # +3 it is the value less three.
  if (identical(item$questionnaire, "mint")) {
    value <- suppressWarnings(as.numeric(given)) + ifelse(wide$format_mint %in% "symmetric7", 3, 0)
    stray <- !is.na(given) & is.na(value)
    if (any(stray)) unread <<- c(unread, paste0(item$key, ": ", given[stray]))
  } else if (item$type %in% c("slider", "curve")) {
    value <- suppressWarnings(as.numeric(sub("%$", "", given)))
  } else {
    said <- vapply(item$options, function(one) {
      if (!is.null(one$text)) one$text else if (!is.null(one$label)) one$label else as.character(one$value)
    }, "")
    values <- vapply(item$options, function(one) if (isTRUE(one$custom)) NA_real_ else as.numeric(one$value), 0)
    given <- as.character(given)
    # A bare number is read as the value, for an option whose words have
    # changed since it was saved.
    numbers <- vapply(item$options, function(one) as.character(one$value), "")
    value <- ifelse(given %in% said, values[match(given, said)], values[match(given, numbers)])
    stray <- !is.na(given) & !given %in% c(said, numbers)
    if (any(stray)) unread <<- c(unread, paste0(item$key, ": ", given[stray]))
  }
  (value - item$lowest) / (item$highest - item$lowest)
}

# A scale is the key without its last part (or its first part, of two).
scale_of <- function(key) {
  parts <- strsplit(key, "_", fixed = TRUE)[[1]]
  paste(parts[-length(parts)], collapse = "_")
}

by_level <- list()
for (item in scale_items) {
  if (!item$key %in% names(wide)) next
  level <- level_keys[item$level]
  column <- setNames(data.frame(reach(item, wide[[item$key]])), item$key)
  by_level[[level]] <- if (is.null(by_level[[level]])) column else cbind(by_level[[level]], column)
}
by_level <- by_level[intersect(level_keys, names(by_level))]
runs_on <- vapply(by_level, function(frame) sum(rowSums(!is.na(frame)) > 0), 0)

# Answers under keys the codebook no longer has: renamed since they were saved.
answered_keys <- setdiff(names(wide)[grepl("^[A-Z][A-Za-z0-9]*_", names(wide))], grep("_RT$", names(wide), value = TRUE))
stale <- setdiff(answered_keys, vapply(codebook$items, function(item) item$key, ""))
stale <- stale[!grepl("^(QC|Feedback|Rating|Level)_", stale)]
```

One radar per level that at least `r MIN_RUNS` runs have answered: a box plot along each ray (median, quartiles, whiskers to 1.5 IQR, points beyond), each item as a share of its own scale, as answered (reversed items not flipped). Nothing joins the rays: neighbouring items are not a continuum. Demographics, free text and right-answer items are left out.

```{r}
#| label: radar

radar <- function(reaches, title) {
  reaches <- reaches[, sort(names(reaches)), drop = FALSE]
  keys <- names(reaches)
  k <- length(keys)
  angle <- pi / 2 - 2 * pi * (seq_len(k) - 1) / k
  at <- function(r) cbind(r * cos(angle), r * sin(angle))
  scales <- vapply(keys, scale_of, "")
  hue <- hcl.colors(length(unique(scales)), "Dark 3")[match(scales, unique(scales))]

  op <- par(mar = c(1, 1, 2, 1), xpd = TRUE)
  on.exit(par(op))
  plot(NULL, xlim = c(-1.5, 1.5), ylim = c(-1.4, 1.4), asp = 1, axes = FALSE, xlab = "", ylab = "")
  title(main = title, font.main = 1, cex.main = 1.1, adj = 0)
  for (r in c(0.25, 0.5, 0.75, 1)) {
    polygon(at(rep(r, k)), border = if (r == 0.5) "grey75" else "grey88", lty = if (r == 0.5) 2 else 1)
  }
  segments(0, 0, cos(angle), sin(angle), col = "grey90")
  text(0.02, c(0.5, 1) + 0.03, c("middle", "top"), cex = 0.6, col = "grey55", adj = 0)

  # A box plot lying along each ray: whiskers, the box between the quartiles
  # as a strip across the ray, the median a bar across it, outliers as points.
  width <- min(0.035, 0.8 / k) # half a box: at most a quarter of the gap between rays at the rim
  for (i in seq_len(k)) {
    given <- reaches[[i]]
    given <- given[!is.na(given)]
    if (!length(given)) next
    stats <- boxplot.stats(given)
    five <- stats$stats
    along <- c(cos(angle[i]), sin(angle[i]))
    across <- c(-along[2], along[1])
    segments(five[1] * along[1], five[1] * along[2], five[5] * along[1], five[5] * along[2], col = hue[i], lwd = 1.2)
    box <- rbind(five[2] * along + width * across, five[4] * along + width * across,
                 five[4] * along - width * across, five[2] * along - width * across)
    polygon(box, col = adjustcolor(hue[i], 0.3), border = hue[i], lwd = 1)
    bar <- rbind(five[3] * along + 1.6 * width * across, five[3] * along - 1.6 * width * across)
    segments(bar[1, 1], bar[1, 2], bar[2, 1], bar[2, 2], col = hue[i], lwd = 2.4)
    if (length(stats$out)) points(stats$out * along[1], stats$out * along[2], pch = 16, cex = 0.6, col = hue[i])
  }

  # Read outwards, never upside down.
  degrees <- angle * 180 / pi
  flip <- cos(angle) < 0
  place <- at(rep(1.06, k))
  for (i in seq_len(k)) {
    text(place[i, 1], place[i, 2], sub("^Opinion_", "", keys[i]), cex = if (k > 30) 0.62 else 0.75, col = hue[i],
         srt = if (flip[i]) degrees[i] + 180 else degrees[i], adj = if (flip[i]) 1 else 0)
  }
}
```

```{r}
#| label: radars
#| results: asis
#| fig-width: 8.5
#| fig-height: 8.5

plotted <- names(runs_on)[runs_on >= MIN_RUNS]
if (!length(plotted)) cat("No level has been answered by", MIN_RUNS, "runs yet.\n")
for (level in plotted) {
  cat("\n\n### ", level, "\n\n", sep = "")
  radar(by_level[[level]], sprintf("%s (%d runs)", level, runs_on[[level]]))
  cat("\n\n")
}
waiting <- names(runs_on)[runs_on < MIN_RUNS]
if (length(waiting)) {
  cat("\n\nNot drawn yet (fewer than ", MIN_RUNS, " runs): ",
      paste(sprintf("%s (%d)", waiting, runs_on[waiting]), collapse = ", "), ".\n", sep = "")
}
```

```{r}
#| label: radars-said
#| results: asis

if (length(unread)) {
  cat("\n\n**Answers not read** (words matching no option of the item in the codebook): ", paste(unique(unread), collapse = "; "), "\n", sep = "")
}
if (length(stale)) {
  cat("\n\n**Keys no longer in the codebook**, left out: ", paste(stale, collapse = ", "), "\n", sep = "")
}
```
